Modeling the impacts of park access on health outcomes: a choice-based accessibility approach

### 2019-06-06 manuscript.Rnw
Rebuilt as a generic manuscript after rejection from EPB.

\documentclass[Crown,sageh,times]{sagej}
\def\journalname{Submitted to Environment and Planning B: Urban Analytics and City Science}

@@

\usepackage{url}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{makecell}

\begin{document}

@@

\author{Gregory S. Macfarlane\affilnum{1}, Nico Boyd\affilnum{2},
John E. Taylor\affilnum{2}, and Kari Watkins\affilnum{2}}
\runninghead{Modeling health outcomes via choice-based accessibility to parks}

\affiliation{\affilnum{1}Civil and Environmental Engineering Department, Brigham Young University\\
\affilnum{2}Fehr \& Peers, Los Angeles, California\\
\affilnum{3}School of Civil and Environmental Engineering, Georgia Institute of Technology}

\corrauth{Gregory Macfarlane: 430 Engineering Building, Provo, UT 84602 USA}
\email{gregmacfarlane@byu.edu}

@@

\keywords{accessibility, spatial modelling, green space}

\maketitle
<<setup, cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE>>=
library(tidyverse)
library(geojsonio)
library(rgdal)
library(rgeos)
library(maptools)
library(spdep)
library(sf)
library(VGAM)
library(qwraps2)
library(knitr)
library(kableExtra)
library(texreg)
library(RSocrata)
library(tidycensus)

@@

\begin{funding}
This project was funded by the Speedwell Foundation.
\end{funding}

>>>>

\documentclass[12]{article}

@@

\usepackage{url}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{makecell}
\usepackage{fullpage}
\usepackage{booktabs}

@@

\author{Gregory S. Macfarlane, Nico Boyd, John E. Taylor, and Kari Watkins}

\begin{document}
\maketitle

@@

<<setup, cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE>>=
library(tidyverse)
library(geojsonio)
library(rgdal)
library(rgeos)
library(maptools)
library(spdep)
library(sf)
library(VGAM)
library(qwraps2)
library(knitr)
library(kableExtra)
library(texreg)
library(RSocrata)
library(tidycensus)

@@

\subsection*{Acknowledgements}
This project was funded by the Speedwell Foundation.
